The Astropy Project

### 2017-10-25 main.tex
UTF-8 input encoding for maintainer's names
Names in registry.json have special characters
update on Overleaf

\documentclass[modern]{aastex61}
\usepackage{hyperref}
\usepackage{xspace}
\usepackage{booktabs}
\newcommand{\escapecmd}[1]{\texttt{\detokenize{#1}}}

@@

\section{Infrastructure for affiliated packages}
\label{sec:infrastructure}
\inlinecomment{BMS}{should we use links to the appropriate github repo?}
\inlinecomment{PLL}{IMHO a list of GitHub repo links for affil. pkgs. should be in appendix, if included.}
\inlinecomment{BMS}{should we describe astropy-helpers even though it's future is unsure?}
%
\par In addition to astronomy related packages and libraries, the \astropy\
Project also contains and supports several infrastructure package that are
very generic. The following sections describes the most widely used
selection of them.
%
\subsection{Package template}
% Brigitta may write this up if there is no other takers
\par \astropy provides a template package that any \python package is welcome to
use (many affiliated packages do so). The template contains a ready-to-go
package layout. It provides infrastructure such as documentation tools,
testing framework and CI templates and configurations, Cython integration,
and documentation on how to make it all work.
%
\subsection{Continuous integration helpers}
% Brigitta
\package{ci-helpers} is a collection of scripts that empowers package
maintainers to control their testing set up and installation process for
various continuous integration services via a set of environment
variables. While the current development is mostly driven by the needs of
the \astropy ecosystem, the actual usage of this package is extremely
widespread. Currently we support setups for Travis CI and Appveyor CI.
%
\subsection{Sphinx extensions}

>>>>

\documentclass[modern]{aastex61}
\usepackage{hyperref}
\usepackage{xspace}
\usepackage{booktabs}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\newcommand{\escapecmd}[1]{\texttt{\detokenize{#1}}}

@@

\section{Infrastructure for affiliated packages}
\label{sec:infrastructure}
\inlinecomment{BMS}{should we use links to the appropriate github repo?}
\inlinecomment{PLL}{IMHO a list of GitHub repo links for affil. pkgs. should be in appendix, if included.}
\inlinecomment{BMS}{should we describe astropy-helpers even though it's future is unsure?}
%
\par In addition to astronomy related packages and libraries, the \astropy\
Project also contains and supports several infrastructure packages that are
very generic. The following sections describes the most widely used
selection of them.
%
\subsection{Package template}
% Brigitta may write this up if there is no other takers
\par \astropy provides a template package that any \python package is welcome to
use (many affiliated packages do so). The template contains a ready-to-go
package layout. It provides infrastructure such as documentation tools,
testing framework and CI templates and configurations, Cython integration,
and documentation on how to make it all work.
%
\subsection{Continuous integration helpers}
% Brigitta
\package{ci-helpers} is a collection of scripts that empowers package
maintainers to control their testing set up and installation process for
various continuous integration services via a set of environment
variables. While the current development is mostly driven by the needs of
the \astropy ecosystem, the actual usage of this package is extremely
widespread. Currently we support setups for Travis CI and Appveyor CI.
%
\subsection{Sphinx extensions}
